CTFEF

### 2023-08-30 Papers/FEDCIS-2023-presentation/sections/CTFEF.tex
more presentation stuff

    \begin{itemize}
        \item Translates source code into Intermidiate Representation\begin{itemize}
            \item Parse
            \item Validate syntax
            \item Inline operators with special syntax (ex: \lstinline|typeof|)
        \end{itemize}
        \item Processes user code and Compiler Interface\begin{itemize}
            \item Compiler interface translates user code into backend Intermidiate Representation
        \end{itemize}
        \item May perform additional processing\begin{itemize}
            \item In C-=-1 it invokes the interpreter to execute metaprogramming code
        \end{itemize}
    \end{itemize}

@@

\begin{frame}
    \frametitle{Intermidiate Representation}

@@

    \begin{itemize}
        \item Operates on Intermidiate Representation 
        \item Uses the same data structures for code and data
        \item Allows executing arbitrary code \begin{itemize}
            \item In practice some operations make sens only at runtime
            \item Some operations must be done slightly differently between runtime and compiletime (ex: memory management)
        \end{itemize}
        \item Must expose api for generating backend IR\begin{itemize}
            \item In case of C-=-1 bindings for parts of LLVM library were created
        \end{itemize}
    \end{itemize}

>>>>

    \begin{itemize}
        \item Translates source code into Intermediate Representation\begin{itemize}
            \item Parse
            \item Validate syntax
            \item Inline operators with special syntax (ex: \lstinline|typeof|)
        \end{itemize}
        \item Processes user code and Compiler Interface \begin{itemize}
            \item Compiler Interface translates user code into backend Intermediate Representation
        \end{itemize}
        \item May perform additional processing\begin{itemize}
            \item In C-=-1 it invokes the interpreter to execute metaprogramming code
        \end{itemize}
    \end{itemize}

@@

\begin{frame}
    \frametitle{Intermediate Representation}

@@

    \begin{itemize}
        \item Operates on Intermediate Representation 
        \item Uses the same data structures for code and data
        \item Allows executing arbitrary code \begin{itemize}
            \item In practice some operations make sens only at runtime
            \item Some operations must be done slightly differently between runtime and compiletime (ex: memory management)
        \end{itemize}
        \item Must expose api for generating backend IR\begin{itemize}
            \item In case of C-=-1 bindings for parts of LLVM library were created
        \end{itemize}
    \end{itemize}
